Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-25 paper/ms.tex
wrote cluster properties section

% NOTE: might want a table of all ages

IC~2602 canonically has an age of $30\pm20\,{\rm Myr}$ (CITE: Van
Leeuwen 2009).
Or logage between 7.533 and 7.563	\citep{bossini_age_2019}.

Or Li age of 40-50Myr (David+19, comparison with other Li stars).

Reported mean metallicity values ${\rm [Fe/H]}$ for the cluster range between
slightly super-solar ($0.04\pm0.01$, \citealt{baratella_gaia-eso_2020}) and
slightly sub-solar ($-0.02 \pm 0.02$, \citealt{netopil_metallicity_2016}).

IC~2602 is supervirial, in the sense that the observed stellar velocity
dispersion is larger than the value expected if it were in virial equilibrium
by about a factor of two \citep{bravi_gaia-eso_2018}.

IC~2602 happens to be near the western edge of the Sco OB2
association, and is relatively close to it in proper motion space
(Damiani+2019).
Damini+2019 also reported evidence for the ongoing evaporation of
\cn, in the form of a diffuse halo of young stars around the central
density cusps.

While \cn\ is older than most known Sco OB2 members,

"""Although IC 2602 does not belong to Sco OB2, it is
spatially and dynamically a close relative, and for this reason
we include it in this work, if even marginally"" (Damiani+2019).
"""We also find that the open cluster IC 2602 has a similar dynamics
to Sco OB2, and its PMS members are currently evaporating and forming
a diffuse (size 10deg) halo around its double-peaked core"""

>>>>

\input{ic2602_ages.tex}

The \cn\ cluster is about 150$\,$pc from the Earth, and is near the
galactic plane with $(l,b)\approx(289.6^\circ, -5.0^\circ)$
\citep{cantatgaudin_gaia_2018}.  It is also sometimes called the
$\theta$ Carinae cluster, after its brightest member.  While \cn\ is
close to the Lower Centaurus Crux subgroup of the Scorpio-Centaurus OB2
association in both position and proper motion space, its older age
and clear kinematic separation indicate that it is a distinct stellar
population \citep{de_zeeuw_hipparcos_1999,damiani_stellar_2019}.

Reliable ages reported for \cn\ range from 30--46$\,$Myr.  We have
collected ages reported over the years in Table~\ref{tab:ages}.  The
Li depletion boundary technique yields slightly older absolute
ages than isochrone fitting.  Rather than redetermine the age of the cluster and add another
line to the table, we simply adopt the absolute age range for \tn\ of
30--46$\,$Myr.

Reported mean metallicity values ${\rm [Fe/H]}$ for the cluster range
between slightly super-solar ($0.04\pm0.01$,
\citealt{baratella_gaia-eso_2020}) and slightly sub-solar ($-0.02 \pm
0.02$, \citealt{netopil_metallicity_2016}).  The extinction $E(B-V)$
is rather low, with reported values ranging from 0.03 to 0.07
\citep[{\it e.g.},][]{randich_gaiaeso_2018}.

Kinematically, IC~2602 seems to be supervirial, in the sense that the
observed stellar velocity dispersion is larger than the value expected
if it were in virial equilibrium by about a factor of two
\citep{bravi_gaia-eso_2018}.  \citet{damiani_stellar_2019} also
reported evidence for the ongoing evaporation of \cn, in the form of a
diffuse $\approx10^\circ$ halo of young stars around the central
density cusps.  A gyrochronological study of these stars could confirm
that these stars are truly coeval with the cluster.
